P2P-LLM: Collaborative LLM Inference

### 2025-05-03 docs/paper/main.tex
MO optimization

A peer-to-peer network is defined as having $n$ nodes in the network. There is an LLM model with $m$ total layers which will be devided between nodes.
Each node $N$ in the network is a tuple $N(\ell, l, c, p)$ where $\ell _i = (x,y) : x,y \in [0,m); y > x$ is the range of layers the node is able to serve, $l_{ij}$ is the network latency between nodes $i$ and $j$,
$c_i$ is the computational cost of the node, measured in miliseconds, and $p_i$ is the price the nodes charges for its compute.

@@

The optimal path is well defined when weights for nodes are clearly defined, but there is not a clear way to define
weights for nodes in this case. In the P2P-LLM network there are two competing criterea that define the weight of node: computational cost and price.
The algorithm described above uses a single objective, while the optimal path in the network is a multi-objective optimization problem.

>>>>

A peer-to-peer network is defined as having $n$ nodes in the network. There is an LLM model with $m$ total layers which will be devided between nodes.
Each node $N$ in the network is a tuple $N(\ell, l, c, p)$ where
\begin{enumerate}
  \item $\ell _i = (x,y) : x,y \in [0,m); y > x$ is the range of layers the node is able to serve
  \item $l_{ij} \in \mathbb{R}$ is the network latency between nodes $i$ and $j$,
  \item $c_i \in \mathbb{R}$ is the computational cost of the node, measured in miliseconds
  \item $p_i \in \mathbb{R}$ is the price the nodes charges for its compute.
\end{enumerate}

@@

The optimal path is well defined when weights for nodes are clearly defined, but there is not a clear way to define
weights for nodes in this case. In the P2P-LLM network there are two competing criterea that define the weight of node: computational cost and price.
The algorithm described above uses a single objective (SO), while the optimal path in the network is a multi-objective (MO) optimization problem.
There are several way to find optimal solutions to MO optimization problems \citep{1599245}. The simplest way is to convert it to a SO optimization problem, and
since the shortest path algorithm is designed for SO objective, it is the most practical solution for this task. In order to reframe the problem as a single objective,
a weighed aggreagte of the objetives is used. In the case for the peer-to-peer network, the SO is a weighed sum of computational cost $c_i$ and price $p_i$.
The objective, or weight of a node, $w_i$ is defined as.
$$w_i = \alpha c_i + 1 - \alpha p_i$$
